An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-08 EconGrowth.Rnw
Now including capability to generate single-country LINEX plots.

<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.">>=
createLinexLatticeGraph()
@

>>>>

<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.", eval=TRUE>>=
createLINEXLatticeGraph()
@

### 2013-03-08 EconGrowthSeminar.Rnw
Now including capability to generate single-country LINEX plots.

\begin{frame}{US: CES and LINEX} %----------------------------
  \begin{columns}[c]
    \column{2.2in}
<<Results_US_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
createCESLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
    \column{2.2in}
<<Results_US_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
#createLINEXLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
\end{frame}

>>>>

\begin{frame}{US: CES and LINEX} %----------------------------
  \begin{columns}[c]
    \column{2.2in}
<<Results_US_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
createCESLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
    \column{2.2in}
<<Results_US_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
createLINEXLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
\end{frame}
